MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-13 MAESTROeX_I/paper.tex
simplified description of Enforce HSE, updated input arguments to only take in rho_0 (since p_0 was only used to get the pressure outside the star, may as well just simply state that)

@@

\item Update $p_0$ by calling
{\bf Enforce HSE}$[p_0^n,\rho_0^{n+1,\star}] \rightarrow [p_0^{n+1,\star}]$.

@@

\item Update $p_0$ by calling
{\bf Enforce HSE}$[p_0^n,\rho_0^{n+1}] \rightarrow [p_0^{n+1}]$.

>>>>

There are a few key numerical modules we use in each time step.
\begin{itemize}
\item {\bf Enforce HSE} computes the base state pressure, $p_0$, from a base state density, $\rho_0$ by integrating the hydrostatic equilibrium condition in 1D (see equation (A10) in \cite{MAESTRO_V}).  The base state pressure remains equal to a constant value from the location of a prescribed cutoff density outward for the entire simulation.
\item {\bf React State}
\end{itemize}

@@

\item Update $p_0$ by calling
{\bf Enforce HSE}$[\rho_0^{n+1,\star}] \rightarrow [p_0^{n+1,\star}]$.

@@

\item Update $p_0$ by calling
{\bf Enforce HSE}$[\rho_0^{n+1}] \rightarrow [p_0^{n+1}]$.
